Revisiting the Austral Spring Extratropical Southern Hemisphere zonally assymetric circulation using complex Empirical Orthogonal Functions

### 2021-08-06 analysis/paper/shceof.Rmd
Apply suggestions from code review

## cEOFs relationship with other variables {#other-variables}

\textcolor{red}{Este título queda raro porque después hablas de modos de variabilidad climática y no de lo que llamaríamos variables}

### SAM

@@

(ref:pp-oceania-cap) Regression of SON mean precipitation anomalies in Oceania (mm per day, shaded) and (column a) cEOF1 the (row 1) Imaginary and (column 1) Real phase. For the 1979 -- 2019.
Areas marked with dots have p-values smaller than 0.05 adjusted for False Detection Rate.

>>>>

## cEOFs relationship with known modes of variability {#other-variables}
### SAM

@@

(ref:pp-oceania-cap) Regression of SON mean precipitation anomalies in Oceania (mm per day, shaded) and (column a) cEOF1 the (row 1) Imaginary and (column 1) Real phase. For the 1979 -- 2019.
Areas marked with dots have p-values smaller than 0.05 adjusted for False Detection Rate.
In black is the West Australia region, defined as the box between `r knitr::combine_words(LonLabel(box_australia$lon))` and `r knitr::combine_words(LatLabel(box_australia$lat))`.
